Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-07-11 articles/formalism/sections/kernel_discussion.tex
refined section on kernel discussion

\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and no scale dependent factor \cite{Zaldarriaga2001a}. Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature with amplitude decaying on increasing angular distance. While we find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$, the function resulting from performing a sliding average on it is seen to scale as $\beta^{-2}$ at intermediate angular separations as seen in \fig{fig:fbeta_avg}, in agreement with the hypothesis made in \cite{Zaldarriaga2001a}. We find that the function resulting from performing a sliding average on ${}_{\md}f$ also shows a similar scaling of $\beta^{-2}$ as seen in \fig{fig:dfbeta_avg}.}

\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning to some lower band limit (determined by the width of the sliding window) radial function from a higher band limit radial function.  On carrying out this moving average on radial functions evaluated with a progressively increasing band limit, one seen that a larger fraction of the radial function matches the scaling of $\beta^{-2}$. Extrapolating this trend to the case of infinite band limit one can see that the behaviour will approach $\beta^{-2}$ across the domain $\beta\in[0,\pi]$.}

\revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function gets modified and is partly responsible for the scaling deviating from the power law. More importantly note that ${}_{\mm}f$ and ${}_{\md}f$ vanish at $\beta=0$ and therefore the sliding average in the vicinity of this point cannot have a power law behaviour of the form $\beta^{-2}$.}

>>>>

\revisit{Here we numerically studied the formally derived radially function ${}_\mm f(\beta)$ which reveals an oscillatory nature with amplitude of the envelope decaying on increasing angular distance at intermediate $\beta$ and increasing as $\beta \rightarrow \pi$. While we find that the positive envelope of ${}_{\mm}f$ scales as $\beta^{-1.55}$ at intermediate $\beta$, the function resulting from performing a sliding average, is seen to scale as $\beta^{-2}$ in this regime as seen in \fig{fig:fbeta_avg}. This is in agreement with the hypothesis made for the flat sky case, where it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to those of $E/B$ modes merely by rotations and no scale dependent factor \cite{Zaldarriaga2001a}. In addition through this exercise we also find that the function resulting from performing a sliding average on ${}_{\md}f$ also shows a similar scaling of $\beta^{-2}$ as seen in \fig{fig:dfbeta_avg}.}

\revisit{In essence the radial function resulting from taking a sliding average can be thought of as transitioning from a higher band limit radial function to a radial function with an effectively lower band limit, set by the width of the sliding window.  On carrying out this moving average on radial functions evaluated with a progressively increasing band limit, it's seen that a larger fraction of the radial function matches the scaling of $\beta^{-2}$. Extrapolating this trend to the case of infinite band it is expected that this behavior will approach $\beta^{-2}$ across the domain $\beta\in[\epsilon,\pi]$ for $\epsilon << 1$.}

\revisit{Near the edges of the domain $\beta \rightarrow 0,\pi$ the window function gets modified and is partly responsible for the scaling deviating from the power law. It is important to note that ${}_{\mm}f$ and ${}_{\md}f$ need to vanish at $\beta=0$ and therefore the sliding average in the vicinity of this point cannot have a power law behavior of the form $\beta^{-2}$.}
